Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
add hr size
fix genetic structure

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
Caribou dig holes, termed craters, in winter to access forage beneath the snow
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
on snow cover and distribution of craters on the landscape.

@@

The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information
in multilayer networks [e.g. @Evans_2020].
We observed seasonal variation in edge overlap. Specifically, we found 
increased edge overlap and graph strength in autumn, winter and spring than in summer 
(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
to seasons of heterogeneous resource availability for caribou [@Peignier_2019]. This analysis
could be extended using time-aggregated networks and a moving-window approach for
informing time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
explicitly considering the temporal context of social interactions in separate
layers, multilayer networks provide a detailed and dynamic perspective of animal
social systems. For example, female mandrill (*Mandrillus sphinx*) sociality is
more completely represented by temporal multilayer networks than aggregated
networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
to temperature and breeding activity. Finally, it is crucial to include
sufficient data within sampling periods or time windows to construct robust
networks [@Farine_2017; @Proskurnikov_2017]. With increasing number of
observations, we found variance decreased in edge overlap and multidegree across
habitat layers and in graph strength within habitat layers (Figure
\@ref(fig:nobs)). As one might expect, dyads that only occasionally associated
were more likely to be recorded with increasing number of observations, demonstrating 
the value of this form of sensitivity analysis to social networks in general
and multilayer networks in particular.

>>>>

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
Caribou dig holes, termed craters, in winter to access forage beneath the snow
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
on snow cover and distribution of craters on the landscape. Home range sizes for 
caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
summer [@Peignier_2019].

@@

The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information
in multilayer networks [e.g. @Evans_2020].
We observed seasonal variation in edge overlap. Specifically, we found 
increased edge overlap and graph strength in autumn, winter and spring than in summer 
(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
to seasons of heterogeneous resource availability for caribou [@Peignier_2019]. This analysis
could be extended using time-aggregated networks and a moving-window approach for
informing time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
explicitly considering the temporal context of social interactions in separate
layers, multilayer networks provide a detailed and dynamic perspective of animal
social systems. For example, female mandrill (*Mandrillus sphinx*) sociality is
more completely represented by temporal multilayer networks than aggregated
networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
to genetic structure. Finally, it is crucial to include
sufficient data within sampling periods or time windows to construct robust
networks [@Farine_2017; @Proskurnikov_2017]. With increasing number of
observations, we found variance decreased in edge overlap and multidegree across
habitat layers and in graph strength within habitat layers (Figure
\@ref(fig:nobs)). As one might expect, dyads that only occasionally associated
were more likely to be recorded with increasing number of observations, demonstrating 
the value of this form of sensitivity analysis to social networks in general
and multilayer networks in particular.
